Disclosure of Product System Models in Life Cycle Assessment: Achieving Transparency and Privacy

### 2018-02-13 revision/rev2-response.tex
reviewer response

@@

At the moment I neglected to include a new section because the paper is already quite long.  But maybe I will change my mind in the next 24 hours.

@@

If I decide to do this, it will be included in the section that Reviewer \#2 wanted me to add at the end of the discussion.

>>>>

Finally, I added a section entitled ``Recommendations to Advance LCA Practice'' at the end of the discussion, to respond to reviewers \#2 and \#3's suggestions about the role of the community and next steps.  This section has added about 400 words to the paper.

@@

As noted in the introduction, I added a new section at the end of the Discussion entitled ``Recommendations to advance LCA practice,'' which addresses this.

@@

As noted in the introduction, I added a new section at the end of the Discussion entitled ``Recommendations to advance LCA practice,'' which addresses this.
